---
title: ""
---
#{.tabset .tabset-fade}
This page will hopefully outline everything one needs to know to get started with the programmatic analysis we use in CVR. 

## Downloading R

- R for [Windows](https://cran.csiro.au/bin/windows/) or [Mac](https://cran.csiro.au/bin/macosx/)
- [RStudio](https://posit.co/download/rstudio-desktop/)

## Installing packages

Most generic packages can be installed using the function

```{r, echo=T, eval=F}
install.packages("readxl")
install.packages("Seurat", version = "5.0.1")

```

<hr>
However, bioinformatic packages are typically stored on bioconductor. When installing an R package from bioconductor, we need to first install BiocManager (a library that allows us to access bioconductor within R)

```{r,echo=T, eval=F}
install.packages("BiocManager")
```

Then we can install packages using:

```{r, eval=F}
BiocManager::install("limma")
```

<hr>

**Packages only need to be downloaded once**. After this, you can **load** only the packages needed for each R session. 

```{r, eval=F}

library(ggplot2)
library(readxl)
library(Seurat)

```


<details><summary>Notes:</summary>
<br>

There is usually always some weird package issues that can occur when you first install packages from bioconductor. If you run into any issues, restart your R session after installing the packages.  

If all else fails - Just use Google!

<hr>

